### 2020-01-08 manuscript/manuscript.rmd
add pairwise comparison of gene overlap (figure)

```{r phylogenetic_signal, fig.width=8, fig.height=15}
#au_tests %>%
#  unite(Matrix, c(manuscript, matrix, model)) %>%
#  group_by(Matrix, result) %>%
#  count() %>%
#  group_by(Matrix) %>%
#  mutate(percent = prop.table(n)) %>%

@@

>>>>

```{r phylogenetic_signal, fig.width=8, fig.height=12}
#au_tests %>%
#  unite(Matrix, c(manuscript, matrix, model)) %>%
#  group_by(Matrix, result) %>%
#  count() %>%
#  group_by(Matrix) %>%
#  mutate(percent = prop.table(n)) %>%

@@

![](figures/Figure_Pairwise_heatmap_animal_root.png)
**Fig XXPairwise_heatmap_animal_root.**
